Spin canonical divisors of log stacky curves

### 2015-06-30 stacky_write_up/spin_cring.tex
Wierd former commit: changes before editing 3.1 seemed to delete some of robin and my changes; I added them back.

\todo{Peter: I think we need something about odd weight modular forms before going right into stacks.}  
Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize Petri's theorem in many \todo{Peter: not clear to me that ``many'' is a good word to use here.  We mostly generalize in one direction}
directions. 
If $X$ is a curve, \todo{why do you start with a curve and then move to a stacky curve? shouldn't it be the opposite order?} then we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$ and {\bf stacky points} $P_1,\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{\geq 2}$ if 
$$\di \sx = \di X \oplus \left(\bigoplus_{i
= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.$$
As is done in Voight and Zureick-Brown \cite{vzb:stacky} one may view a stacky curve as a stack, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of ``fractional points,'' i.e., stacky points. A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $\Delta \in \di X$ is an effective divisor and $2\halfcan = K_X + \Delta + \sum_{i=1}^{r}\subhalf{e_i}P_i.$
The central object of study in this paper is the {\bf log spin
canonical ring} of $(\sx, \Delta, \halfcan)$ is
\begin{align*}
	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx,\lfloor d \halfcan \rfloor)
\end{align*}

In particular, we would like to bound the degrees in which the
graded ring and its relations are generated. The work by O'Dorney
shows that the canonical ring of any $\BQ$-divisor $D =
\frac{\alpha_1}{\beta_1}P_1 + \frac{\alpha_2}{\beta_2}P_2$ of
$\BP_k^1$ with $\# \Supp(D) \leq 2$ is generated in degrees up
to $e := \max(\beta_1, \beta_2)$ with relations generated in
degrees up to $2e$ \cite[Section 4]{dorney:canonical}. Furthermore,
O'Dorney gives a larger bound when the support of $D$ is allowed to
have arbitrarily many points in terms of least-common-multiples.
Voight and Zureick-Brown also bounded the generator and relation
degrees of log spin canonical rings of $(\sx, \Delta, \halfcan)$,
in the case that genus is positive and $\halfcan$ is effective,
by $3e$ and $6e$ for $e := \max(e_1, \ldots, e_r)$.

@@

\begin{defn}
We equip the polynomial ring $k[x_1, \ldots, x_n]$ with the
(weighted graded) reverse lexicographic order \textbf{grevlex}
$\prec$: if 
\[
	x^{\vec{m}} = \prod_{d,i} x_{d,i}^{m_{d,i}}
\]

\noindent
and $x^{\vec{n}}$ are monomials in $k[x]_{\vec{a}}$, then $x^{\vec{m
}} \succ x^{\vec{n}}$ if and only if either
\begin{equation}
\vec{a}\cdot\vec{m} = \sum_{d,i} dm_{d,i}  > \vec{a} \cdot \vec{n}
\end{equation}
or
\begin{equation} \label{eqn:grevlexdef}
\text{$\vec{a}\cdot\vec{m} = \vec{a} \cdot \vec{n}$ and the last (right-most) nonzero entry in $\vec{m}-\vec{n}$ is negative.}
\end{equation}
It is important to note that in \eqref{eqn:grevlexdef}, the ordering of the variables matters: it corresponds to a choice of writing the exponents of a monomial as a vector.  A common choice for us will be
\begin{equation} \label{eqn:xdOrder}
 x_{1,1}^{m_{1,1}} \cdots x_{D,a_D}^{m_{D,a_D}} \leftrightarrow (m_{D,1},\dots,m_{D,a_D},\ldots,m_{1,1},\dots,m_{1,a_1}) 
 \end{equation}
in which case we have $x_{2,1} \succ x_{1,2}^2$
and $x_{5,1} \succ x_{1,6}^2 x_{3,2}$, etc.
We indicate this ordering in the presentation of the ring, e.g.~for the above we would write
\[ k[x]_{\vec{a}}= k[x_{1,1},\dots,x_{1,a_1},\dots,x_{D,1},\dots,x_{D,a_D}]. \]
In this way, our relations write generators in larger degree in terms of those in smaller degree (``later generators in terms of earlier generators''), which gives the most natural-looking canonical rings to our eyes.
\end{defn}

For a homogeneous polynomial $f \in k[x]_{\vec{a}}$, we define the \textbf{initial term} $\initial_{\prec}(f)$ to be the monomial in the support of $f$ that is largest with respect to $\prec$, and we define $\initial_{\prec}(0)=0$.  Let $I \subseteq k[x]_{\vec{a}}$ be a homogeneous ideal.  We define the \textbf{initial ideal} $\initial_{\prec}(I)$ to be the ideal generated by $\{\initial_{\prec}(f) : f \in I\}$.  A \textbf{Gr\"obner basis} (also called a \textbf{standard basis}) for $I$ is a set $\{f_1,\dots,f_n\} \subset I$ such that 
\[ \langle \initial_{\prec}(f_1),\dots,\initial_{\prec}(f_n) \rangle = \initial_{\prec}(I). \]

@@

\noindent
be the positive best lower approximations of $\frac{
\alpha}{\beta}$. Note that the elements $t_1,\ldots, t_{\lfloor d_i \frac{\alpha}{\beta}\rfloor}$ in $(R_{\halfcan})_{d_i}$ with $\ord_P^{\halfcan'}(t_i) = i$ are linearly independent over $(R_{\halfcan'})_d$. Hence, by a dimension count, these sections form a $k$-basis for
$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.

%For any $1\le i < j \le n$, we have $\frac{c_i}{d_i} < \frac{c_j}{d_j}$.  
Choose a positive best lower approximation $\frac{c_i}{d_i}$.  Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = d_i$ and $\deg(z_j)<d_i$ for all $j\in \{1, \ldots r\}$. Then for each $j$, \todo{Aaron: I don't see why either of the next 2 claims hold, but maybe I'm being silly.}
\[
	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{d_i},
\]

\noindent
so
\[
	-\ord^{\halfcan'}_P \left(\prod_{j=1}^n z_j \right) = \sum_{j=1}^n -\ord^{\halfcan'}_P(z_j) < c_i .
\]

@@

Using Equation ~\ref{eqn:c-from-lower-terms}, we recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$. Define 
\[
	S_0 = \{u^l : l\in \mathbb{Z}_{\ge 0}\}
\]
and for each $i \in \mathbb{N}$, suppose $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i.$ Note that such a $c_j$ exists because $1=c_1\le i.$ Define
\[
	S_i = y_j S_{i-j}.
\]
Observe that this recursive definition ensures that $S_i$ contains only elements $z\in R_\halfcan$ satisfying $-\ord^{\halfcan'}_P(z)=i$. \todo{Perhaps it's worth reminding the reader here that $y_i$ are as in the statement of (a) and have order $-c_i$.}
Then define 
\[
	S = \cup_{i=1}^{\infty} S_i.
\]
Note that $S_0$ is not part of this union and in fact $S\cap S_0 = \emptyset$ by pole order considerations.

Applying Equation \ref{eqn:c-from-lower-terms}, we see that $S$ contains elements in degree $d\in \mathbb{N}$ with each pole order in $\{1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor\}$. \todo{Maybe we should make reference these generating the desired lattice, as described in Evan's paper? I think this is basically a rehashing of Evan's 1-point case?} Thus, by dimension counting, $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, and we have proven part (a).

@@

One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and that of Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky} is that 
%in \cite{vzb:stacky}, Voight and Zureick-Brown may assume that $\{P_i\} \cap \Supp(K_X) = \emptyset.$ 
we cannot assume that $\{P_i\} \cap \Supp(L_X) = \emptyset$, as $H^0(X, L_X)$ may have no global sections.  We circumvent this issue by working with orders of zeros and poles relative to the divisor we are inducting from, instead of relative to the structure sheaf.

\begin{defn}
\label{defn:admissible}
Let $(\sx', \Delta, L'),(\sx, \Delta , L)$ be log spin
curves, with the same stacky points $Q_1, \ldots, Q_r$. Let $J \subset
\{1, \ldots, r\}$. Suppose $e_i'+ 2 \chi_J (i) = e_i$ where

$$\chi_J(i) = \begin{cases}
	1, &\text{ if }i \in J\\
	0, &\text{ otherwise. } 
\end{cases}$$

Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx',L',J)$
to be {\bf admissible} if the $R'$ admits a presentation
\begin{align*}
	R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i, e_i'}]_{i \in J} \right)/I'
\end{align*}

\noindent
with $y_{i, e_i'} \in R'$ for each $i \in J$ such that the following
three conditions hold.

\todo{Peter:I'm still kind of unhappy with the notation $y_{e_i'}$ because it is treating $e_i'$ like a formal object rather than a number. What I mean is if $e_1'=e_2'$ that a reader might reasonably interpret $y_{e_1'}$ the same as $y_{e_2'}$. Aaron: By all means, please suggest better notation and we can discuss it. However, I think your particular concern is well answered because we include the further subscript $i$. That is, $y_{1,e_1} \neq y_{2,e_2}$ even if $e_1 = e_2=5$, because $y_{1,5}$ and $y_{2,5}$ are different variables. Another thing to note here is that $e_i' = e_i + 2,$ so that the two will never be equal. Does this assuage your concern? Also, Further, when I read David's paper, he used this notation, and I was never confused by this notation.}
\begin{enumerate}
	\item[(Ad-i)] First, 
	\begin{align*}
	\deg y_{e_i'} &= e_i'  &\text{ and } &&-\ord_{Q_i}^{\halfcan_X'}(y_{i, e_i'})
		= \frac{e_i'- 1}{2}.
	\end{align*}
		\item[(Ad-ii)] Second, every generator $z \neq y_{i, e_i'}$	of $R'$ satisfies
		\begin{align*}
			\frac{-\ord_{Q_i}
^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] Third, we have
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i - e_j'\}
		\end{align*}
\end{enumerate}
\end{defn}

\begin{rem}
Note that $S_{\sigma,J}(i,d-1)$ as defined in condition (Ad-iii) of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
\end{rem}

@@

\begin{rem}
\label{rem:three-cases}
For the purposes of our induction, carried out in Theorems ~\ref{thm:g-high-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-0-main}, we will often add in a single
stacky point with stabilizer order $3$. Say $(\sx,\Delta,\halfcan)$ is a log spin
curve with signature $\sigma = (g;e_1,\ldots, e_r,\delta) = (g;3,\ldots, 3,
\delta)$. We will need to deal with signatures $\sigma$ satisfying one of the following three cases, which we will soon refer to in Lemma ~\ref{lem:raise-stacky-order}:
\begin{enumerate}
	\item $g = 0, e_1 = \cdots = e_r = 3, \delta = 0$ and $r \geq 5$
	\item $g = 1, e_1 = \cdots = e_r = 3, \delta = 0,$ and $ r \geq 2$
	\item $g \geq 2, e_1 = \cdots = e_r = 3, \delta$ arbitrary, and $r \geq 1$.
\end{enumerate}
\end{rem}

We next come to Lemma ~\ref{lem:raise-stacky-order}, which is an
analog of ~\cite[Theorem 8.5.7]{vzb:stacky}

@@

\begin{defn}
\label{defn:lower-ideal}
Suppose $X$ is a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K+\Delta$. Choose generators $x_1, \ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1, \ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$. Let $I_{L,d}$ be the $d$th graded piece of $I_L$ and define
$$J_{L,d} = \sum_{j = 1}^{d- 1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j}.$$
\end{defn}

>>>>

\todo{Peter: I think we need something about odd weight modular forms before going right into stacks.}  
Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize Petri's theorem in many \todo{Peter: not clear to me that ``many'' is a good word to use here.  We mostly generalize in one direction}
directions. 
If $X$ is a curve, \todo{why do you start with a curve and then move to a stacky curve? shouldn't it be the opposite order?} then we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$ and {\bf stacky points} (also called {\bf{fractional points}}) $P_1,\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{\geq 2}$ if 
\[
\di \sx = \di X \oplus \left(\bigoplus_{i
= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.
\]
\todo{Peter: Would it be better to say $Div(\sx)=(Div(X))[\frac{1}{e_i}P_i]_{1\le i\le r}$ or something like that?}
As is done in Voight and Zureick-Brown \cite{vzb:stacky} stacky curves may be formalized as stacks, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of stacky points. \todo{I don't know if this is a good statement to make.  We aren't really viewing $\sx$ as a scheme.  Rather we're are determining information about its canonical rings through knowledge of scheme data.}  A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $\Delta \in \di X$ is an effective divisor and $2\halfcan = K_X + \Delta + \sum_{i=1}^{r}\subhalf{e_i}P_i.$
The central object of study in this paper is the {\bf log spin
canonical ring} of $(\sx, \Delta, \halfcan)$ is
\begin{align*}
	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx,\lfloor d \halfcan \rfloor)
\end{align*}

In particular, we would like to bound the degrees in which the
graded ring and its relations are generated.  O'Dorney
shows that the canonical ring of any $\BQ$-divisor $D =
\frac{\alpha_1}{\beta_1}P_1 + \frac{\alpha_2}{\beta_2}P_2$ of
$\BP_k^1$ is generated in degrees up
to $e := \max(\beta_1, \beta_2)$ with relations generated in
degrees up to $2e$ \cite[Theorem 6]{dorney:canonical}. Furthermore,
O'Dorney gives a larger bound in terms of least common multiples of the denominators when the support of $D$ is allowed to
have arbitrarily many points.
Voight and Zureick-Brown also bounded the generator and relation
degrees of log spin canonical rings of $(\sx, \Delta, \halfcan)$,
in the case that genus is positive and $\halfcan$ is effective,
by $3e$ and $6e$ for $e := \max(e_1, \ldots, e_r)$.

@@

First, we give a definition of the graded degree of a monomial
in a graded polynomial ring.

 \begin{defn}
\label{defn:monomial-degree}
Let $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a graded polynomial
ring and let $\alpha := \prod_{i = 1}^{n} x_{d_i, i}^{f_i} \in
k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a monomial. Then
we define
\[
	\deg \alpha := \sum_{i = 1}^{n} d f_i
\]
\end{defn}

Now define the (graded) lexicographic order \textbf{grlex}
$\prec_{\text{grlex}}$ on a polynomial ring $k[x_{d_1, 1}, \ldots,
x_{d_n, n}]$ to be the monomial ordering such that:

\begin{defn}
\label{defn:grlex}
If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
\succ_{\text{grlex}} \beta$ if either $\alpha$ has larger degree:
\begin{equation}
\deg \alpha := \sum_{i = 1}^{n} d f_i  > \sum_{i = 1}^{n} d f_i' =: \deg \beta
\end{equation}
or $\alpha$ is larger using the lexicographical ordering event of equal
degrees:

\begin{equation}
\label{eqn:grlex-tie}
	\deg \alpha = \deg \beta \text{ and }
	\alpha \succ_{\text{lex}} \beta
\end{equation}
\end{defn}

We can equip the polynomial ring $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$
-with the (weighted graded) reverse lexicographic order
-\textbf{grevlex} $\prec_{\text{grevlex}}$ as follows:
-
-\begin{defn}
-\label{defn:grevlex}
-If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
-^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
-monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
-\succ_{\text{grevlex}} \beta$ if either $\alpha$ has larger degree:
-
-\begin{equation}
-	\deg \alpha := \sum_{i = 1}^{n} d f_i  > \sum_{i = 1}^{n} d f_i' =: \deg \beta
-\end{equation}
-or $\alpha$ has a smaller right-most entry in the event of equal
-degrees:
-
-\begin{equation}
-\label{eqn:grevlex-tie}
-	\deg \alpha = \deg \beta \text{ and }	f_i - f_i' < 0 \text{ for
-the	largest } i \text{ such that } f_i \neq f_i'
-\end{equation}
-\end{defn}

We can equip the polynomial ring $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$
with the (weighted graded) reverse lexicographic order
\textbf{grevlex} $\prec_{\text{grevlex}}$ as follows:

\begin{defn}
\label{defn:grevlex}
If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
\succ_{\text{grevlex}} \beta$ if either $\alpha$ has larger degree:

\begin{equation}
	\deg \alpha := \sum_{i = 1}^{n} d f_i  > \sum_{i = 1}^{n} d f_i' =: \deg \beta
\end{equation}
or $\alpha$ has a smaller right-most entry in the event of equal
degrees:

\begin{equation}
\label{eqn:grevlex-tie}
	\deg \alpha = \deg \beta \text{ and }	f_i - f_i' < 0 \text{ for
the	largest } i \text{ such that } f_i \neq f_i'
\end{equation}
\end{defn}

\begin{rem}
Note that the ordering of the variables matters in both
Equation ~\ref{eqn:grlex-tie} and Equation ~\ref{eqn:grevlex-tie}.
\end{rem}

Our inductive arguments in Section ~\ref{sec:induction} will
usually have an inclusion $R \supset R'$ of log spin canonical
rings such that $R'$ is generated by elements $x_{d_i, i}$ and $R$
is generated over $R'$ by elements $y_j$. In these cases, it is
natural to consider term orders which treat these sets of variables
separately. We now present the \textbf{block term order} introduced
by Voight and Zureick-Brown \cite[Section 8.1]{vzb:stacky}.

\begin{defn}
\label{defn:block-order}
Let $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$ and $k[y_{c_1, 1}, \ldots,
y_{c_m, m}]$ be weighted polynomial rings with existing term
orders $\prec_x$ and $\prec_y$, respectively. Let $\alpha :=
\prod_{i = 1}^{n} x_{d_i, i}^{f_i}$ $\prod_{j = 1}^{m} y_{c_j, j}
^{h_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}
\prod_{j = 1}^{m} y_{c_j, j}^{h_i'}$ be monomials in $k[x_{d_1, 1},
\ldots, x_{d_n, n}] \otimes$ $k[y_{d_1', 1}, \ldots, y_{d_m', m}]$.
Let $\alpha_x := \prod_{i = 1}^{n} x_{d_i, i}^{f_i}$ be the
part of $\alpha$ in $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$ and
likewise with $\alpha_y$, $\beta_x$, and $\beta_y$.

In the \textbf{(graded) block} (or \textbf{elimination}) term
ordering on $k[x_{d_1, 1}, \ldots, x_{d_n, n}] \otimes k[y_{d_1', 1},
\ldots, y_{d_m', m}]$, we define $\alpha \succ \beta$ if
  \begin{enumerate}
  \item[(i)] $\deg \alpha  > \deg \beta$ or
  \item[(ii)] $\deg \alpha = \deg \beta$ and 
    \begin{enumerate}
    \item $\alpha_y \succ_y \beta_y$ or
    \item $\alpha_y =  \beta_y$ and $\alpha_x \succ_x \beta_x$
    \end{enumerate}
  \end{enumerate}
\end{defn}

\todo{write below part}
For a homogeneous polynomial $f \in k[x]_{\vec{a}}$, we define the \textbf{initial term} $\initial_{\prec}(f)$ to be the monomial in the support of $f$ that is largest with respect to $\prec$, and we define $\initial_{\prec}(0)=0$.  Let $I \subseteq k[x]_{\vec{a}}$ be a homogeneous ideal.  We define the \textbf{initial ideal} $\initial_{\prec}(I)$ to be the ideal generated by $\{\initial_{\prec}(f) : f \in I\}$.  A \textbf{Gr\"obner basis} (also called a \textbf{standard basis}) for $I$ is a set $\{f_1,\dots,f_n\} \subset I$ such that 
+\[ \langle \initial_{\prec}(f_1),\dots,\initial_{\prec}(f_n) \rangle = \initial_{\prec}(I). \]

@@

\noindent
be the positive best lower approximations of $\frac{
\alpha}{\beta}$. Note that the elements $t_1,\ldots, t_{\lfloor d_i \frac{\alpha}{\beta}\rfloor}$ in $(R_{\halfcan})_{d_i}$ with $\ord_P^{\halfcan'}(t_i) = i$ are linearly independent over $(R_{\halfcan'})_d$. Hence, by a dimension count, these sections form a $k$-basis for
$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.\todo{take out two sentences}

%For any $1\le i < j \le n$, we have $\frac{c_i}{d_i} < \frac{c_j}{d_j}$.  
Choose a positive best lower approximation $\frac{c_i}{d_i}$.  Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = d_i$ and $\deg(z_j)<d_i$ for all $j\in \{1, \ldots r\}$. Observe that $\frac{c_i}{d_i}$ is a best lower approximation for $\frac{\alpha}{\beta}$ and $\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)}< \frac{\alpha}{\beta}$, for each $j$.  Hence, for each $j$, 
\[
	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{d_i},
\]
so the mediant inequality tells us
\[
	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{d_i}.
\]
Multiplying through by $d_i$ gives
\[
	-\ord^{\halfcan'}_P \left(\prod_{j=1}^n z_j \right) = \sum_{j=1}^n -\ord^{\halfcan'}_P(z_j) < c_i .
\]

@@

Using Equation ~\ref{eqn:c-from-lower-terms}, we recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$. Define 
\[
	S_0 = \{u^l : l\in \mathbb{Z}_{\ge 0}\}
\]
and for each $i \in \mathbb{N}$, suppose $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i.$ Note that such a $c_j$ exists because $1=c_1\le i.$ Define
\[
	S_i = y_j S_{i-j}.
\]
Observe that this recursive definition ensures that $S_i$ contains only elements $z\in R_\halfcan$ satisfying $-\ord^{\halfcan'}_P(z)=i$. \todo{Perhaps it's worth reminding the reader here that $y_i$ are as in the statement of (a) and have order $-c_i$.}
Then define 
\[
	S = \cup_{i=1}^{\infty} S_i.  
\]\todo{make equation and reference}
Note that $S_0$ is not part of this union and in fact $S\cap S_0 = \emptyset$ by pole order considerations.

Applying Equation \ref{eqn:c-from-lower-terms}, we see that $S$ contains elements in degree $d\in \mathbb{N}$ with each pole order in $\{1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor\}$. \todo{Maybe we should make reference these generating the desired lattice, as described in Evan's paper? I think this is basically a rehashing of Evan's 1-point case?} Thus, by dimension counting, $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, and we have proven part (a) \todo{why follows from 3.1}.

@@

One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and that of Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky} is that 
%in \cite{vzb:stacky}, Voight and Zureick-Brown may assume that $\{P_i\} \cap \Supp(K_X) = \emptyset.$ 
we cannot assume that $\{P_i\} \cap \Supp(L_X) = \emptyset$, as $H^0(X, L_X)$ may have no global sections.  We circumvent this issue by working with the orders of zeros and poles relative to the divisor we are inducting from, rather than relative to the structure sheaf.\todo{Peter: This last sentence is kind of awkward.  I changed ``instead of relative to the structure sheaf'' to ``rather than relative to the structure sheaf,'' but it can still be made to sound cleaner... I hope...}

\begin{defn}
\label{defn:admissible}
Let $(\sx', \Delta, L'),(\sx, \Delta , L)$ be log spin
curves, with the same course space $X$ and stacky points $Q_1, \ldots, Q_r$. Let $J \subset
\{1, \ldots, r\}$. Suppose $e_i'+ 2 \chi_J (i) = e_i$ where

\[
\chi_J(i) = \begin{cases}
	1, &\text{ if }i \in J\\
	0, &\text{ otherwise. } 
\end{cases}
\]

Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx',L',J)$
to be {\bf admissible} if $R'$ admits a presentation
\begin{align*}
	R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i, e_i'}]_{i \in J} \right)/I'
\end{align*}

\noindent
with each $y_{i, e_i'}$ viewed in $R'$ through the image of this isomorphism and such that for each $i \in J$ such that the following
three conditions hold:
\begin{enumerate}
	\item[(Ad-i)] First, 
	\begin{align*}
	\deg y_{e_i'} &= e_i'  &\text{ and } &&-\ord_{Q_i}^{\halfcan_X'}(y_{i, e_i'})
		= \frac{e_i'- 1}{2}.
	\end{align*}
		\item[(Ad-ii)] Second, every generator $z \in \{x_1, \ldots, x_m\} \cup \{y_{j,e_ij'}: j\in J - \{i\} \}$ satisfies
		\begin{align*}
			\frac{-\ord_{Q_i}
^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] Third, we have
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i - e_j'\}
		\end{align*}
\end{enumerate}
\end{defn}

\begin{rem}
Note that $S_{\sigma,J}(i,d-1)$ as defined in condition (Ad-iii) of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
\end{rem}
\todo{Peter: I'm not sure how useful this remark is.  After seeing the definition of $S_{\sigma, J}(I,d)$ a reader will probably be a little mystified why it is a useful condition.  The inclusion of the relationship to something defined in VZB that also seems ad hoc and that they probably will not have seen may not be the most helpful use of this space.}

@@

\begin{rem}
\label{rem:three-cases}
For our inductive arguments in Theorems ~\ref{thm:g-high-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-0-main}, we will often add in a single
stacky point with stabilizer order $3$. Say $(\sx,\Delta,\halfcan)$ is a log spin
curve with signature $\sigma = (g;e_1,\ldots, e_r,\delta) = (g;3,\ldots, 3,
\delta)$, and our base cases include signatures $\sigma$ characterized by one of the following: cases, which we will soon refer to in Lemma ~\ref{lem:raise-stacky-order}:
\begin{enumerate}
	\item $g = 0, e_1 = \cdots = e_r = 3, \delta = 0$ and $r \geq 5$
	\item $g = 1, e_1 = \cdots = e_r = 3, \delta = 0,$ and $ r \geq 2$
	\item $g \geq 2, e_1 = \cdots = e_r = 3, \delta$ arbitrary, and $r \geq 1$.
\end{enumerate}
\end{rem}

We next come to Lemma ~\ref{lem:raise-stacky-order}, which is an
analog of ~\cite[Theorem 8.5.7]{vzb:stacky}.

@@

\begin{defn}
\label{defn:lower-ideal}
Suppose $X$ is a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K+\Delta$. Choose generators $x_1, \ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1, \ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$. Let $I_{L, d}$ be the $d$th graded piece of $I_L$ and define
\[
	J_{L,d} = \sum_{j = 1}^{d- 1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j}.
\]
\end{defn}
